The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-05-10 paper.tex
Edit intro and math section.

The degree of control over single photons has also improved. Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum, new ways to engineer entangled quantum states and implement quantum operations have been discovered. These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time,

In Section \ref{sec:math}, ...
And in Section \ref{sec:encoding}

@@

A single photon in a quantum interferometer is described by its creation and annihilation operators, $\adagh_{j}$ and $\hat{a}_j$ respectively, where $j$ is the mode label of the interferometer. These operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$. The action of a $2d$-port linear optical interferometer that has an equal number of input and output ports is expressed as an application of unitary operations on the creation operators,
\begin{align}
b_i^{\dag}=\sum_{j=1}^d U_{ij}a_j^\dag \ ,
\end{align}
where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in SU(d)$. All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994}. By convention, the interferometer is assumed to act only on the spatial mode of the input state.

Additional quantum labels (represented by $\alpha, \beta$) are added on when other degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present:
\begin{align}
[\ah_{j,\alpha},\adagh_{k,\beta}]=\delta_{j,k}\delta_{\alpha,\beta}\ .
\end{align}
As a consequence, quantum interference between multiple photons only occur when all quantum labels are the same.
In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons as a sequence of beamsplitters and internal transformations. Toolkits using group theory are being developed to deal with partial distinguishabilities among interfering photons \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}. Others use quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}. \sihui{Experimental implementation [Walmsley, Jennewein]}

@@

\section{Efficient circuit decompositions of linear optics networks}

>>>>

The degree of control over single photons has also improved. Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, new ways to engineer entangled quantum states and implement quantum operations have been discovered. These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time. We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons.
And in Section \ref{sec:encoding}

@@

A single photon in a quantum interferometer is described by its creation and annihilation operators, $\adagh_{j}$ and $\hat{a}_j$ respectively, where $j$ is the mode label of the interferometer. These operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$. The action of a $2d$-port linear optical interferometer that has an equal number of input and output ports is expressed as an application of unitary operations on the creation operators,
\begin{align}
b_i^{\dag}=\sum_{j=1}^d U_{ij}a_j^\dag \ ,
\end{align}
where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in SU(d)$. All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994} (see Section \ref{sec:decomp}). By convention, the interferometer is assumed to act only on the spatial mode of the input state.

Additional quantum labels are added to the creation and annihilation operators when other degrees of freedom, such as polarization, orbital angular momentum, and time-bins, are present. In this case, their commutator relation is
\begin{align}
[\ah_{j,\alpha},\adagh_{k,\beta}]=\delta_{j,k}\delta_{\alpha,\beta}\ ,
\end{align}
where $\alpha$ and $\beta$ represent these other degrees of freedom. As a consequence, quantum interference between multiple photons only occur when all quantum labels are the same. It is also possible to derive an analogous decomposition to that of Reck {\it et al.~}that realizes the unitary transformation on such photons as a sequence of beamsplitters and internal transformations. Toolkits using group theory are being developed to deal with partial distinguishabilities among interfering photons \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}. Others use quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}. \sihui{Experimental implementation [Walmsley, Jennewein]}

@@

\section{Efficient circuit decompositions of linear optics networks}\label{sec:decomp}
